Adolescent well-being in the digital age

### 2022-03-24 00-clean.Rmd
Fix synthetic data gen

```{r create-mock-gwp-data}
#| eval: false
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
library(synthpop)
gwp_syn <- gwp %>% 
  drop_na()
gwp_syn <- syn(
  gwp_syn %>% filter(outcome == "Life_satisfaction"), 
  method = c("", "", "", "", "", "normrank", "normrank"),
  # visit.sequence = c(1:6, 8, 7),
  maxfaclevels = 168
  )
saveRDS(gwp_syn, gwp_mock_path)
```

```{r}
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```

>>>>

```{r mock-gwp-data}
gwp_mock_path <- "data-raw/gwp-MOCK.rds"
if (dir.exists("data-raw/Gallup") & !file.exists(gwp_mock_path)) {
  library(synthpop)
  gwp_syn <- gwp %>% 
    drop_na()
  gwp_syn <- syn(
    gwp_syn, 
    method = c("", "", "", "", "", "", "normrank", "normrank"),
    maxfaclevels = 168
  )
  saveRDS(gwp_syn, gwp_mock_path)
}

# Load if actual data doesn't exist
if (!dir.exists("data-raw/Gallup")) {
  cat("Using synthetic GWP data.")
  gwp <- read_rds(gwp_mock_path)
} else {
  cat("Using actual GWP data.")
}
```
